---
title: "Multiple Model Analysis"
author: "Bryan Alcorn and Todd Vogel"
output: ioslides_presentation
---

## Introduction 

Statistical Analysis project with the goal of comparing multiple linear models for the Balance variable in credit data.

We will examing the following models to try and apply to future credit card data to estimate balance numbers.

1. Ordinary Least Squared
2. Lasso 
3. Ridge
4. Principal Component Regression
5. Partial Least Squared Regression


## Data

We have a data set containing variables that relate to credit. 

**4 Qualitative Variables**
1. Gender
2. Student
3. Married Ethnicity 

**7 Quantitative Variables**
1. Income
2. Limit
3. Rating
4. Cards
5. Age
6. Education
7. Balance

We trained ou models with a set of 300 points and tested on 100 points taken randomly from the original Credit.csv data

## Analysis 

```{r, echo = FALSE}
load('../data/MSE_ols.RData')
load('../data/MSE_ridge.RData')
load('../data/MSE_pcr.RData')
load('../data/mse_lasso.RData')
load('../data/mse_plsr.RData')
load('../data/ols_model.RData')
load('../data/ridge_model.RData')
load('../data/lasso_model.RData')
load('../data/pcr_model.RData')
load('../data/plsr_model.RData')

library(xtable)
library(Matrix)
options(xtable.caption.placement = 'top', xtable.comment = FALSE)
```

```{r, echo=FALSE, xtable, results='asis'}
Variables <- c("Intercept", "Income","Limit", "Rating", "Cards", "Age", "Education", "GenderFemale", "StudentYes", "MarriedYes", "EthnicityAsian", "EthnicityCaucasian")
OLS <- as.vector(ols_coef)
Ridge <- as.vector(best_model_ridge)
Lasso <- as.vector(bestmodel_lasso)
PCR <- as.vector(pcr_coef)
PCR <- append(PCR, 0, 0)
PLSR <- as.vector(plsr_coef)
PLSR <- append(PLSR, 0, 0)

Coef.frame <- data.frame(Variables, OLS, Ridge, Lasso, PCR, PLSR)

Coef_table <- xtable(Coef.frame, caption="Information about Model Coefficients", digits = 3)
print(Coef_table, type="latex")

```

```{r}
Coef_table <- xtable(Coef.frame, caption="Information about Model Coefficients", digits = 3)
print(Coef_table, type="latex")
```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

## Model Coefficients

## Model MSE 



