---
output: pdf_document
---

# Results

```{r, echo = FALSE}
setwd("/Users/toddvogel/Documents/Senior Year/stat159-fall2016-project2/report/sections")

load('../../data/MSE_ols.RData')
load('../../data/MSE_ridge.RData')
load('../../data/MSE_pcr.RData')
load('../../data/mse_lasso.RData')
load('../../data/mse_plsr.RData')
load('../../data/ols_model.RData')
load('../../data/ridge_model.RData')
load('../../data/lasso_model.RData')
load('../../data/pcr_model.RData')
load('../../data/plsr_model.RData')

library(xtable)
library(Matrix)
options(xtable.caption.placement = 'top', xtable.comment = FALSE)
```

```{r, echo=FALSE, xtable, results='asis'}
MSE <- c(MSE_ols, MSE_ridge, lasso_mse, MSE_pcr, plsr_mse)
Model <- c('OLS', 'Ridge', 'Lasso', 'PCR', 'PLSR')
mse.frame <- data.frame(Model, MSE)

MSE_table <- xtable(mse.frame, caption="Information about Mean Squared Errors", digits = 3)
print(MSE_table, type="latex")
```




```{r, echo=FALSE, results='asis'}
Variables <- c("Intercept", "Income","Limit", "Rating", "Cards", "Age", "Education", "GenderFemale", "StudentYes", "MarriedYes", "EthnicityAsian", "EthnicityCaucasian")
OLS <- as.vector(ols_coef)
Ridge <- as.vector(best_model_ridge) 
Ridge <- append(Ridge, 0, 0)
Lasso <- as.vector(bestmodel_lasso) 
PCR <- as.vector(pcr_coef) 
PCR <- append(PCR, 0, 0)
PLSR <- as.vector(plsr_coef) 
PLSR <- append(PLSR, 0, 0)

Coef.frame <- data.frame(Variables, OLS, Ridge, Lasso, PCR, PLSR)

Coef_table <- xtable(Coef.frame, caption="Information about Model Coefficients", digits = 3)
print(Coef_table, type="latex")
