# Results

After forming the aforementioned regression models we found 12 coefficients that represent the best fit for each model. The resulting predictive function looks like:

$$Y = \beta_) + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + \beta_4 X_4 + \beta_5 X_5 + \beta_6 X_6 + \beta_7 X_7 + \beta_8 X_8 + \beta_9 X_9 + \beta_{10} X_{10} + \beta_{11} X_{11} + \beta_{12} X_{12}$$

```{r, echo = FALSE}
load('../data/MSE_ols.RData')
load('../data/MSE_ridge.RData')
load('../data/MSE_pcr.RData')
load('../data/mse_lasso.RData')
load('../data/mse_plsr.RData')
load('../data/ols_model.RData')
load('../data/ridge_model.RData')
load('../data/lasso_model.RData')
load('../data/pcr_model.RData')
load('../data/plsr_model.RData')

library(xtable)
library(Matrix)
options(xtable.caption.placement = 'top', xtable.comment = FALSE)
```

```{r, echo=FALSE, xtable, results='asis'}
Variables <- c("Intercept", "Income","Limit", "Rating", "Cards", "Age", "Education", "GenderFemale", "StudentYes", "MarriedYes", "EthnicityAsian", "EthnicityCaucasian")
OLS <- as.vector(ols_coef)
Ridge <- as.vector(best_model_ridge) 
Lasso <- as.vector(bestmodel_lasso) 
PCR <- as.vector(pcr_coef) 
PCR <- append(PCR, 0, 0)
PLSR <- as.vector(plsr_coef) 
PLSR <- append(PLSR, 0, 0)

Coef.frame <- data.frame(Variables, OLS, Ridge, Lasso, PCR, PLSR)

Coef_table <- xtable(Coef.frame, caption="Information about Model Coefficients", digits = 3)
print(Coef_table, type="latex")

```

This table presents the fit between the prediction variables and the response variable (`Balance`) determined from the `cv.glmnet()`, `pcr()`, and `plsr()` functions, for each of our 5 models (OLS, Ridge, Lasso, PCR, PLSR). 


After finding the 5 predictive functions, we found the MSE's for each model:

```{r, echo=FALSE, results='asis'}
MSE <- c(MSE_ols, MSE_ridge, lasso_mse, MSE_pcr, plsr_mse)
Model <- c('OLS', 'Ridge', 'Lasso', 'PCR', 'PLSR')
mse.frame <- data.frame(Model, MSE)

MSE_table <- xtable(mse.frame, caption="Information about Mean Squared Errors", digits = 3)
print(MSE_table, type="latex")
```

Analysis of these numbers will reveal which model has the most predictive power.



